### 2022-12-02 proof.tex
details
up

\section{Decidability}

@@

>>>>

\section{Decidability for WSTS with downward/strong upward compatibility}

@@

If 
$A \cap J \subseteq I$,
then
${\uparrow (A \cap J)} \subseteq {\uparrow I} = I$.
However
$({\uparrow A}) \cap J \subseteq {\uparrow (A \cap J)}$.
Indeed if $x$ in $({\uparrow A} \cap J)$,
$x$ is in $\uparrow A$
so there exists $a \in A$ such that $x \geq a$.
However $x$ is also in $J$, meaning $a$ is in $J$.
Meaning $a$ is in $(A \cap J)$
and $x \in { \uparrow (A \cap J)}$.

In the other direction,
since $A \subseteq {\uparrow A}$,
$({\uparrow  A}) \cap J \subseteq I$ implies
$A \cap J \subseteq ({\uparrow  A}) \cap J \subseteq I$.
\end{proof}
